Cells at War: The Playfulness of Game-Based Learning

### 2023-06-07 cellsatwar_bus_presentation/beap_pres_dec.tex
BUS PRESENTATION READY TO GO
updates for western conference

% Bibliography stuff
\usepackage[natbib=true, sorting=nyt, style=authoryear-comp]{biblatex}
\addbibresource{ABC1.bib}

%Extra packages
\usepackage{makecell}

@@

			\footnotetext[1]{\tiny\cite{brown1989situated, jan2016game}}
		\end{itemize}

@@

	\footnotetext[2]{\tiny\cite{coller2009effectiveness, tomavska2022let}}

@@

	\footnotetext[3]{\tiny\cite{lister2015gamification,mayer2010adding,molin2017role,fishman2014empowering}}

@@

	\section{Acknowledgements}
	\begin{frame}{Acknowledgements}
		\begin{columns}
			\begin{column}{0.45\textwidth}
				Thank you...
				\begin{itemize}
					\item Dr. Rosa da Silva
					\item Jean Paul Amore
					\item Bianca Flaim
					\item Oluwalonimi Ayekun
					\item Jennifer Luk
					\item The Entire George Brown College team
					\item CEWIL Canada	
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\centering
				\includegraphics[width=2cm, height=1cm]{gbc.png}	
				\includegraphics[width=5cm, height=2cm]{cewil.jpg}
			\end{column}
		\end{columns}

>>>>

% Bibliography stuff
\usepackage[backend=biber, giveninits=true, doi=false, isbn=false, natbib=true, url=true, eprint=false, style=numeric, sorting=nyt, sortcites=ynt, maxcitenames=2, maxbibnames=10, minbibnames = 10, uniquename=false, uniquelist=false]{biblatex} % can change the maxbibnames to cut long author lists to specified length followed by et al., currently set to 99.
\addbibresource{ABC1.bib} % The filename of the bibliography
%Extra packages
\usepackage{makecell}

@@

		\tiny\footcite{brown1989situated, jan2016game}
		\end{itemize}

@@

	{\tiny\footcite{coller2009effectiveness, tomavska2022let}}

@@

	{\tiny\footcite{lister2015gamification,mayer2010adding,molin2017role,fishman2014empowering}}

@@

	\section{Acknowledgements}
	\begin{frame}{Acknowledgements}
		\begin{columns}
			\begin{column}{0.45\textwidth}
				Thank you...
				\begin{itemize}
					\item Dr. Rosa da Silva
					\item Jean Paul Amore
					\item Bianca Flaim
					\item Oluwalonimi Ayekun
					\item Jennifer Luk
					\item The Entire George Brown College team
					\item CEWIL Canada	
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\centering
				\includegraphics[width=4cm, height=5cm]{credits.png}
				\includegraphics[width=2cm, height=1cm]{gbc.png}	
				\includegraphics[width=4cm, height=1cm]{cewil.jpg}
			\end{column}
		\end{columns}
	\end{frame}

	\section{References}
	\begin{frame}[allowframebreaks]
		\frametitle{References}
		\nocite{*}
		\printbibliography[heading=none, sorting=nyt]
		\newpage
	\end{frame}
